\section{Data}
% What is the data?
The dataset contains various features about match outcomes, schedule, game specifics and team characteristics from the
first soccer division in Switzerland. The data is collected from $2005/2006$ until $2021/2022$ and includes 2500
matches and 100 variables.

% Table: team summary
Table \ref{tab:team-summary} reports aggregated information of all the teams which are participating in the Swiss soccer
league concerning the points in combination with their relative expensiveness. The teams are ordered by the average points
per match.

% Table: team summary
From a first glance the relationship between the proportion of matches where the visting team had a higher market value ($ratio_more_expensive$)
than the home team and the average points per match is not obvious. The first three teams are concordant in the average
scores per match and the $ratio_more_expensive$ variable but the remaining teams do not exhibit this clear trend. However,
higher points per match seem to be more frequent with higher valued visiting teams.

% Table: market-value-summary
Table \ref{tab:market-value-summary} reports descriptive statistics of a selection of variables by the two status of
the visiting team being higher valued than the home team. The variables displayed have been chosen according to the
correlation between the status of the visiting team being higher valued than the home team and the average points per match.

It can be seen, that the average team market value for a higher valued visiting team is roughly two times higher than
the lower team. A similar relation can be observed with the average points of the visiting team, which is approximately
twice as high for the visiting team, if it is considered as a higher valued team.
Another interesting observation is average number of national players in a higher valued visiting team, which obviously
corresponds with national players having a higher market value.

% Plot:
Figure \ref{fig:scatter} reveals how the points per match vary with respect to visiting team being more expensive or not.
The red dot marks the average points per match for the respective category. 3-point matches seem to be more frequent
with higher valued visiting teams.




